plots with prolactin

### 2019-12-02 analysis/16_PRL.Rmd
fixed lay icon

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
    geom_boxplot() +
  ylim(c(-10,120)) + 
    mytheme() +
  #theme(axis.text.x = element_blank()) + 
  theme(legend.position = "none") + 
  labs(x = "parental care stages", y = "prolactin conc. (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5)
p1

p2 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = as.numeric(treatment), y = plasma_conc)) +
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    mytheme() +
    theme(axis.text.x = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin conc. (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "parental care stages", y = "prolactin conc. (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.8) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -3.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.6) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.4) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.4) + 
  ylim(c(-10,120)) 
p2
```

>>>>

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
    geom_boxplot() +
  ylim(c(-10,120)) + 
    mytheme() +
  #theme(axis.text.x = element_blank()) + 
  theme(legend.position = "none") + 
  labs(x = "parental care stages", y = "prolactin conc. (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5)
p1

p2 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = as.numeric(treatment), y = plasma_conc)) +
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    mytheme() +
    theme(axis.text.x = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin conc. (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "parental care stages", y = "prolactin conc. (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.8) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.8) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.6) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.4) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.4) + 
  ylim(c(-10,120)) 
p2
```

```{r PRL.pit}
vsd.pit <- readvsd("../results/04_vsd_pit.csv")
colData.pit <- readcolData("../results/04_colData_pit.csv")
geneinfo <- read_csv("../metadata/00_geneinfo.csv") %>%  dplyr::select(Name, geneid, entrezid) %>% arrange(Name)
candidategenes <- c("PRL")
candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)

p3 <- ggplot(candidates.pit, aes(x = as.numeric(treatment), y = PRL)) + 
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment, alpha = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    mytheme() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "PRL expression in the pituitary", x = "parental care stage") +
    scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9),
                       labels = charlevels) +
  annotation_custom(control, ymin = 12, ymax = 14, xmin = -7.8) +
  annotation_custom(bldg, ymin = 12, ymax = 14, xmin = -5.8) +
  annotation_custom(lay, ymin = 12, ymax = 14, xmin = -3.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = -1.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 0.6) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 2.4) +
  annotation_custom(hatch, ymin = 12, ymax = 14, xmin = 4.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 6.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 8.4)  + 
  ylim(c(13,24)) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) 
p3
```
